### 2019-11-24 paper/introduction.tex
my part in #27

Various previous works explore starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while few focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
fissile materials (except $^{233}$U) has not been studied before. Therefore,
the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U. Two different feed mechanisms were selected:

>>>>

Various previous works explore starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while few focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
fissile materials (except $^{233}$U) has not been studied before. Therefore,
the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \footnote{Reactor-grade Pu is a mixture of Pu isotopes chemically extracted from PWR SNF with 33 GWd/tHM burnup} \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U. Two different feed mechanisms were selected:
